Specific leaf area explains difference in biomass partitioning between woody plant functional types

### 2014-10-07 manuscript/draftpaper.tex
Added bib file with many allometry studies

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}

@@

Friend et al. (2014) showed that 30\% of the uncertainty in global vegetation carbon simulated with seven vegetation models is due to the residence time of carbon in vegetation. This residence time depends on turnover rates of the various plant pools, and hence also on the distribution of biomass between these pools. For example, vegetation with a higher leaf mass fraction will have a lower overall residence time of carbon.

@@

Enquist & Niklas (2002) report 2.6 times higher leaf mass at given stem mass for conifers compared to angiosperms, but did not separate further, nor interpreted this difference in terms of SLA. Their interpretation is 'that conifers typically retain three cohorts of leaves that have less well-developed [...] mesophyll'. Not sure how that latter bit makes sense, and leaf lifespan interpretation is no good; because it still begs the question why would conifers not simply have 1/3 less leaf mass per cohort?

@@

@@

@@

>>>>

\usepackage{amssymb,amsmath}
\usepackage{palatino}
\usepackage{framed}
\usepackage{parskip}
\usepackage{geometry}
\geometry{verbose,tmargin=3cm,bmargin=3cm,lmargin=3cm,rmargin=3cm}
\bibliographystyle{authordate1}

@@

Friend et al. (2014) showed that 30\% of the uncertainty in global vegetation carbon simulated with seven vegetation models is due to the residence time of carbon in vegetation. This residence time depends on turnover rates of the various plant pools, and hence also on the distribution of biomass between these pools. For example, vegetation with a higher leaf mass fraction will have a lower overall residence time of carbon. Study was \cite{friend_carbon_2014}.

@@

Enquist and Niklas (2002) report 2.6 times higher leaf mass at given stem mass for conifers compared to angiosperms, but did not separate further, nor interpreted this difference in terms of SLA. Their interpretation is 'that conifers typically retain three cohorts of leaves that have less well-developed [...] mesophyll'. Not sure how that latter bit makes sense, and leaf lifespan interpretation is no good; because it still begs the question why would conifers not simply have 1/3 less leaf mass per cohort?

@@

O'Neill and DeAngelis (1981) reported much higher leaf biomass for gymnosperms vs. angiosperms, at a given woody biomass increment. This means (as Niklas reported) a much higher productivity per unit leaf biomass for angiosperms.

@@

Hui et al 2014 - isometric scaling of above vs. belowground biomass in chinese forest biomass database.

Sardans and Penuelas 2013 - report similiar LMF for evergreen angio. and gymnosperms, and ca. 40\% less leaf mass for decid. angio. Local study, 3000 plots in Catalonia.

Reich et al 2014 : "On average, when standardized for MAT and Mstem, conifers tended to have more Mfol and less Mroot than angiosperm forests". Their Fig. 2 shows trends in LMF with MAT etc., in bins of stem size. Also allometric analysis with MAT as covariate, showing significance of MAT. For Angiosperms, our explanation would be that evergreen angio is more common at high MAT. But what about conifers?

@@

\section{References}
\bibliography{allometry}
